How wise is the crowd: Can we infer people are accurate and competent merely because they agree with each other?

### 2024-11-04 paper.Rmd
update paper revisions round 1
before proof, make compatible with up-to-date R version

affiliation:
  - id            : " "
    institution   : " "

@@

keywords          :

@@

# RQ2 (as separate t-test):
accuracy <- t.test(confidence ~ number, data = exp1, paired = TRUE)
competence <- t.test(competence ~ number, data = exp1, paired = TRUE)

@@

exp1_research_questions <- list(
  # RQ1
  model_small_accuracy = text_ready(model_small_accuracy),
  model_large_accuracy = text_ready(model_large_accuracy),
  model_small_competence = text_ready(model_small_competence),
  model_large_competence = text_ready(model_large_competence),
  # speparate t-tests for RQ2
  means = exp1 %>% 
    group_by(number) %>% 
    summarise(across(c(confidence, competence), 
                     mean)) %>% 
    rounded_numbers() %>% 
    split(.$number), 
  accuracy = clean_t_test(accuracy), 
  competence = clean_t_test(competence),
  # RQ2 and RQ3 in a single mixed model
  model_interaction_competence = text_ready(model_interaction_competence), 
  model_interaction_accuracy = text_ready(model_interaction_accuracy),
  # Exploratory analysis
  exploratory_analysis = text_ready(exploratory_analysis)
)
```

@@

The distributions presented were similar to those of Experiment 1, although generated in a slightly different manner (see ESM, section \@ref(exp3)). Each participant rated four scenarios, two for each level of convergence. By contrast to experiment one, all scenarios only involved groups of three informants.

@@

```{=tex}
\clearpage
\newpage
```
```{r child = "appendix_simulations.Rmd"}
```

>>>>

author: 
  - name          : "Jan Pfänder"
    affiliation   : "1"

  - name          : "Benoît De Courson"
    affiliation   : "2"

  - name          : "Hugo Mercier"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "hugo.mercier@gmail.com"
    address: " "

affiliation:
  - id            : "1"
    institution   : "Institut Jean Nicod, Département d’études cognitives, ENS, EHESS, PSL University, CNRS, France"
  - id            : "2"
    institution   : "Max Planck Institute for the Study of Crime, Security and Law, Freiburg im Breisgau, Germany"

authornote: |
  We thank the anonymous reviewers for their very valuable feedback. HM received funding from the ANR (SCALUP, ANR-21-CE28-0016-01), and from the John Tempelton Foundation ("An Evolutionary and Cultural Perspective on Intellectual Humility via Intellectual Curiosity and Epistemic Deference"). The ANR also supported this project through FrontCog (ANR-17-EURE-0017), and PSL (ANR-10-IDEX-0001-02).

@@

keywords          : consensus, convergence, majority rules, competence, trust in science

@@

# RQ2 (as separate t-test):
# accuracy <- t.test(confidence ~ number, data = exp1, paired = TRUE) 
# competence <- t.test(competence ~ number, data = exp1, paired = TRUE)

@@

exp1_research_questions <- list(
  # RQ1
  model_small_accuracy = text_ready(model_small_accuracy),
  model_large_accuracy = text_ready(model_large_accuracy),
  model_small_competence = text_ready(model_small_competence),
  model_large_competence = text_ready(model_large_competence),
  # speparate t-tests for RQ2
  means = exp1 %>% 
    group_by(number) %>% 
    summarise(across(c(confidence, competence), 
                     mean)) %>% 
    rounded_numbers() %>% 
    split(.$number), 
  # accuracy = clean_t_test(accuracy), 
  # competence = clean_t_test(competence),
  # RQ2 and RQ3 in a single mixed model
  model_interaction_competence = text_ready(model_interaction_competence), 
  model_interaction_accuracy = text_ready(model_interaction_accuracy),
  # Exploratory analysis
  exploratory_analysis = text_ready(exploratory_analysis)
)
```

@@

The distributions presented were similar to those of Experiment 1, although generated in a slightly different manner (see ESM, section \@ref(exp3)). Each participant rated four scenarios, two for each level of convergence. By contrast to Experiment 1, all scenarios only involved groups of three informants.

@@

\clearpage
\newpage

```{r child = "appendix_simulations.Rmd"}
```
